Designing for Multiple Use and At-Risk Users: Tor Configuration Launcher

### 2016-03-31 pets2017-paper/pets2017-paper.tex
notes to self on TODOs

\subsection{Results}

@@

\section{Related Work}

\section {Acknowledgments}

>>>>

\subsection{Results} 
{\color {red} This will be the main part of the paper--where we report on the data that we collected through the xlab experiment. Some of the questions we want to answer are: did the new interface improve success rate? did the new interface only help certain people? Did people take longer or shorter in the new version? Did we shift participants' behaviors in the new interface? Are the way people approach trying different configurations affected? are there existing problems for both interfaces? (we know for sure that users still not receiving feedback is an issue. I don't know how many of our participants actually saw our helpful error messages, since they took minutes to pop up, and some never pop up at all..)}

@@

\section{Related Work} 
{\color {red} TODO}

\section {Acknowledgments}
{\color {red} TODO}
